---
title: "Leaflet"
author: "Abhinav Swain"
date: "25/10/2021"
output: html_document
---

### Overview
This project was created as part of the Developing Data Products course of the Coursera Data Science Specialization. The goal of the project is to create a web page using R Markdown that features a map created with Leaflet, and to host the resulting web page on either GitHub Pages, RPubs, or NeoCities.

### Load the necessary packages
```{r}
library(leaflet)
```
###Cherry Blossom Festivals and Viewing Locations in Japan
```{r}
map <- leaflet() %>% addTiles() %>%
addMarkers(lat=40.557802, lng=139.982561, popup = "Hirosaki Park, Hirosaki") %>%
  addMarkers(lat=35.686736, lng=139.711640, popup = "Shinjuku Gyoen, Tokyo") %>%
addMarkers(lat=35.522839, lng=139.660901, popup = "Mitsuike Koen, Yokohama") %>%
addMarkers(lat=35.409498, lng= 138.869329, popup = "Chureito Pagoda, Fuji Five Lakes") %>%
addMarkers(lat=34.808590, lng=135.532601, popup = "Expo 70 Commemorative Park, Osaka") %>%    

addMarkers(lat= 37.407871, lng=140.500588, popup = "Mihara Takizakura, Fukushima")  
map
```

